
---
title: "RM_HW_W10_2"
author: "Rekha Murali"
date: "3/28/2019"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Follow up to question 3
### Seurat processing
#### some parts take a while so I am not knitting this part
```{}
# seurat processing
WT_seurat <- FindVariableFeatures(object = WT_seurat, 
  selection.method = 'mean.var.plot', mean.cutoff = c(0.0125, 3), 
  dispersion.cutoff = c(0.5, Inf))
  
length(x = VariableFeatures(object = WT_seurat))
VariableFeaturePlot(WT_seurat)

# regress out UMI and mitoDNA
WT_seurat <- ScaleData(object = WT_seurat, 
features = rownames(x = WT_seurat), 
  vars.to.regress = c("nCount_RNA", "fraction.mito"))


WT_seurat <- RunPCA(object = WT_seurat, 
features = VariableFeatures(object = WT_seurat), verbose = FALSE)
ElbowPlot(object = WT_seurat, ndims=20)
WT_seurat<- FindNeighbors(object = WT_seurat, dims = 1:6)
WT_seurat <- FindClusters(object = WT_seurat, resolution = 1)
WT_seurat <- RunTSNE(object = WT_seurat, dims = 1:6)

saveRDS(WT_seurat,"/Users/rekhamurali/Desktop/lab/0327_WT_seurat_processed.rds")

```

# view clusters
```{r}
suppressPackageStartupMessages(library(Seurat))
WT_seurat <- readRDS("/Users/rekhamurali/Desktop/lab/0327_WT_seurat_processed.rds")
DimPlot(object = WT_seurat, reduction = 'tsne')
```
### Explanation

I show 7 distinc clusters here but I also did not mess much with the parameters so this would need to be refined. Considering I might only be looking for one cell type this might not even make sense.


# view expression of potential markers 

## validate first hypothesis

```{r}
FeaturePlot(WT_seurat, reduction = "tsne", features = "CHGA")
```


### Explanation

This hypothesis was probably wrong, I should see CHGA in more cells if it were endocrine.

## cell cycle gene
```{r}
FeaturePlot(WT_seurat, reduction = "tsne", features = "TOP2A")
```

### Explanation

Since it is a homoegenous population, I would expect the cells to cluster based on cell cycle. We do see pretty high expression of TOP2A so there are clearly a lof of clusters which are cycling. 



## Test another hypothesis
### These are some genes in a module defining salivary gland epithelial cells

```{r}
FeaturePlot(WT_seurat, reduction = "tsne", features = "CNN1")
FeaturePlot(WT_seurat, reduction = "tsne", features = "PDPN")
FeaturePlot(WT_seurat, reduction = "tsne", features = "ACTB")
FeaturePlot(WT_seurat, reduction = "tsne", features = "TPM1")

```



## explanation

Source: 

http://biocc.hrbmu.edu.cn/CellMarker/search.jsp?species=Human&tissue=Salivary%20gland&cellname=Epithelial%20cell


You can see that I have expression of a lot of them, and while not all of them are tissue specific this could be a starting place. Some of the genes, such as CNN1 and TPM1 are expressed mostly in smooth muscle. TPM1 especially is highly expressed in muscle tissues. I don't have a concrete conclusion, but maybe this is a little more correct.



